A Multi-telescope Campaign on FRB 121102: Implications for the FRB Population

### 2017-08-07 referee_response.txt

General comments:

We thank the referee for a thoughtful review and suggestions for improvement. We have made almost all the recommended changes. In a few cases, we have responded with an explanation of why no change was made or given our interpretation of the suggestion for a change.

@@

I think this work is worthy of publication in the journal with moderate revision of the manuscript. Some moderate revision of the text is needed (see below) as well as some structural and conceptual changes. I have included my comments on the manuscript below with general large comments (1, 2, 3..) on the paper at the beginning, and major (A, B, C,...) and minor (i, ii, iii,...) comments per section.

General comments on the manuscript:

1. Throughout the text it is mentioned that this is the first simultaneous detection of an FRB pulse at multiple observatories, but I don't believe this is correct. The observations detailed in Marcote et al. 2017 include VLBI observations of individual pulses from FRB 121102 detected at different observatories. In that sense, this paper does not present the first simultaneous detection. Perhaps the authors mean first simultaneous detection at multiple radio frequencies, but if this is the case this statement should be revised throughout the manuscript.

>>> We do believe the VLA+AO burst is the first of its kind both as a multi-frequency and as a multi-telescope detection. The first VLA+Arecibo burst was detected on 17 September, while the bursts reported in Marcote et al were detected on 20 September. The publication date of the VLA+AO (discussed in Chatterjee et al 2017) and EVN bursts were simultaneous, so it is also not true that one was published first. We would prefer to keep the current wording, but we have made small changes to highlight the novelty of multi-frequency detections, as suggested below.

@@

2. While the simultaneous detection of an FRB pulse at multiple frequencies is indeed quite interesting I would argue that the _non-detections_ while observing with the VLA and other telescopes is also extremely important and stick out to me as a key result of this paper. This isn't well highlighted in the abstract or the text of the paper and throughout the manuscript these non-detections are not presented in a straightforward way. The observations are reported as "simultaneous coverage" without mention of detection or non-detection (although non-detection is implied). In a revised version of the manuscript it would be valuable to see these non-detections presented more centrally and directly -- see individual sections for locations where this would be particularly helpful to the reader.

>>> We will work to raise the profile of the nondetection results as suggested. We have done that throughout the text by modifying the use of "simultaneous" and "detection/non-detection".

@@

3. In the text it is written that the Arecibo data are recorded with full Stokes polarization intensity. A bright (39-sigma) pulse was detected at Arecibo in this observing mode but no pulse polarization information is presented here. If pulse polarization information is available for this burst it should absolutely be included in this paper! If for some reason the polarization could not be calibrated or cannot be presented here the reason should be included somewhere in the manuscript.

>>> There is indeed a lot of work to be done on the Arecibo data and we wish to treat that as a whole. That observing campaign is ongoing and multiple students are working on it. We defer detailed Arecibo analysis for future work, as noted here as "Michilli et al, in prep". This paper focused largely on the VLA data analysis and the timing and spectral information derived from comparison to other observatories.

@@

>>> Done.

Observations:

Figure 1: This figure is very busy and difficult to parse. I would suggest the following changes:
- Change the symbols for each observing epoch to the number of bursts detected in that observation (0, 1, 2, etc)
- Create two extra rows and plot the VLA observations at L-band, S-band, and C-band separately
- Next to the name of each telescope on the right hand side of the figure (or replacing the name of the telescope) provide the observing frequency, e.g. LWA (70 MHz), VLA (1.4 GHz), VLA (3 GHz), VLA (4.5 GHz), etc.
- Use circles to indicate overlapping frequency coverage and dispense with bold circles and dashed lines
- Use a solid line to indicate the observation where a burst was detected at both VLA and Arecibo

>>> Figure 1 is fairly dense and takes time to interpret, but we feel it best represents the complexity of the observing campaign at a birds eye view. The main point is to highight the amount of observing (over time and frequency) and when/where detections were made. The addition of a new table of observing set up should also help in interpretation of this figure.

@@

ii. "signals" : signal

iii. "Two of the VLA ... had simultaneous coverage with the LWA1" : Here again please be clear about the non-detection with the LWA1.

iv. "up to 48 seconds" : What is the motivation for searching up to 48 seconds in width? Are there physical justifications for searching for such long duration signals in time?

>>> Done. On the last point, the long search duration is standard for the search pipeline and may detect highly-scattered bursts. However, it is more appropriate for other kinds of transients.

@@

Equation 1: A is typically used for a unitless amplitude, but in this case is given in units of flux density. If this value is indeed meant to be the flux density of the pulse then $S$ should be used as the symbol for flux density instead of A.

>>> Done.

A. Paragraph beginning "The parameters for the best model ... " : Your fits to the pulse spectra seem to indicate that all but two of the VLA burst detections are well-modeled by a Gaussian envelope completely contained within the 3 GHz band. How likely is this? It seems to be implying that 3 GHz was the perfect frequency at which to center your observations. While this seems fortunate it doesn't make immediate physical sense to me. I might have expected some uniformly broadband pulses, some with an envelope within your observing band, and some with an envelope that extends beyond the observing band, but you find that most are described by an entirely in-band envelope. Is this physical or could this be an artefact of the model fits you have applied to the data? If you believe that this is indeed an intrinsic effect I would like to see more discussion of the physical mechanism behind the very fortunate 3 GHz observing window.

>>> Our interpretation is that this is a detection bias and has no physical meaning. If the bursts have a peak in their spectrum, then it is easiest to detect bursts with a peak inside the observing band. Spectral peaks outside or at the edge of the band have reduced measured flux and lower significance. This was also noted in the pre-localization papers on FRB 121102 by Spitler et al and Scholz et al.

@@

Table 2: Footnote labeling: The labeling here is not consistent with the labeling used in Table 1.

>>> The addition of the last footnote requires this set of footnotes to be in a different order than in Table 1. It is not possible to include all this information with the same footnote marks as in Table 1.

@@

i. "While most bursts are modeled ... into two subbursts." : This particular burst may be an outlier in this sample of bursts but it is not unique among the bursts detected from FRB 121102 which has many bursts that seem to be composed of interesting substructure. A sentence or two putting this particular pulse in that context would be useful.

>>> We have added a reference to Spitler et al and Scholz et al, which noted multi-burst structure. Other references are possible in unpublished Arecibo data, but there is nothing citable to discuss.

@@

Figure 4: Are each of the bursts plotted here dedispersed to the best-fit DM given in Table 2 or dedispersed to the best-fit DM of FRB 121102 of 560.5 pc/cm^3? If the former, what effect does it have on the spectrum of each pulse to force them all to a DM = 560.5 pc/cm^3? Is the structure you are seeing in the spectrum highly dependent on the DM fit?

>>> The spectra are extracted from a single integration at the best-fit (SNR maximizing) DM for plotting purposes. Since this varies from burst to burst, using a single DM would effectively cut some flux out from the peak integration. In that sense, the plotted spectrum is sensitive to the DM. For modeling purposes, we use the full dynamic spectrum, so all flux from the burst is included.

### 2017-08-07 repeater-vladata.tex
ready to resubmit

Observations in August and September were searched by a prototype version of \textit{realfast}\footnote{See \url{http://realfast.io} \citep{2017AAS...22933002L}.}, a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} \citep{2015ApJ...807...16L}.}. Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$. Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration. A flux scale was calculated for each spectral window from an observation of 3C48 and applied to all burst spectra and has an accuracy of about 10\%.

@@

While most bursts are modeled with well-defined parameter probability distributions, one burst is an outlier. Figure \ref{fig:corner} shows the scatter plot matrix \citep{corner} for the MCMC run on burst 57646. Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM. This shows that the model is not appropriate for this burst and could indicate that the burst can be decomposed into two subbursts.

@@

\software{\emph{rtpipe}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}, emcee \citep{2013PASP..125..306F}}

>>>>

Observations in August and September were searched by a prototype version of \textit{realfast}\footnote{See \url{http://realfast.io} \citep{2017AAS...22933002L}.}, a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe} \citep{2017ascl.soft06002L}. Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$. Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration. A flux scale was calculated for each spectral window from an observation of 3C48 and applied to all burst spectra and has an accuracy of about 10\%.

@@

While most bursts are modeled with well-defined parameter probability distributions, one burst is an outlier. Figure \ref{fig:corner} shows the scatter plot matrix \citep{corner} for the MCMC run on burst 57646. Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM. This shows that the model is not appropriate for this burst and could indicate that the burst can be decomposed into two subbursts, as has been noted before for \frb\ \citet{2016Natur.531..202S, 2016arXiv160308880S}.

@@

\software{\emph{rtpipe} \citep{2017ascl.soft06002L}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}, emcee \citep{2013PASP..125..306F}}
